Type theories as quotient inductive-recursive types

### 2025-02-14 tex/main.tex
fix typo

The elimination principle says that the functions $\elim_{\Ctx}$, $\elim_{\Sub}$, $\elim_{\Ty}$ and $\elim_{\Tm}$ as soon as motives and methods are given.
\LT[noinline]{says what?}

>>>>

The elimination principle says that there are functions $\elim_{\Ctx}$, $\elim_{\Sub}$, $\elim_{\Ty}$ and $\elim_{\Tm}$ as soon as motives and methods are given.
